\documentclass[11pt]{article}
\usepackage{fullpage}
\topmargin0.25in

\begin{document}
\thispagestyle{empty}
\sloppy

\begin{center}
\Large \bf Budget Justification
\end{center}
\vspace{0.2in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{A: Senior Personnel (co-PI: Matthew Moore)}
%\hfill \\
%\noindent
The requested senior personnel funding is to support one month of 
co-PI Moore's summer salary in each of years 1--3. During this period, the PIs
will work together to develop and implement algorithms, write papers,
and work closely with the graduate student. 
Co-PI Moore's salary will in years 1,2,3 will be USNA Step 30, 31, and 32 respectively, with the monthly salaries listed in the table:
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3  & Total \\
    \hline
    co-PI Moore & $\$9,585$ & $\$9,762$ & $\$9,977$  & $\$29,324$ \\
    \hline
  \end{tabular}
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{C: Fringe Benefits}
The fringe benefits of co-PI Moore at USNA are 34\%. 
In addition a COLA of 3\% is added to estimate the cost of living increase government works may receive in January. \\
%\hfill \\
\begin{center}
  \begin{tabular}{|c|r|r|r|r|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    co-PI Moore Fringe & $\$3,259$ & $\$3,319$ & $\$3,392$ & $\$9,970$ \\
    \hline
    co-PI Moore COLA & $\$288$ & $\$293$ & $\$299$ & $\$880$ \\
    \hline
    Total & $\$3,546$ & $\$3,612$ & $\$3,692$ & $\$10,850$ \\
    \hline
  \end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{E: Domestic Travel}
%\hfill \\
%\noindent
The requested travel funds is to partially fund a domestic trip
for co-PI Moore in years 2 and 3.  The expected costs per
conference participant is $\$1,750$ with a breakdown of $\$600$ for
airfare, $\$750$ for lodging, $\$56$ for local transportation, $\$144$
for meals (four days at $\$36$ per day), and $\$200$ for conference
registration.  Potential meeting venues include several SIAM Meetings
(Annual Meetings, CSE, Dynamical Systems), APS Fluids Meetings, or
appropriately themed workshops. 
Alternatively, co-PI Moore may use these travel funds to visit PI Quaife and the funded graduate student at FSU in order to collaborate on the project.
Travel funds for the first year are removed due to the COVID crisis.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Year 1 & Year 2 & Year 3 & Total \\
    \hline
    Domestic Travel &  & $\$1,000$ & $\$1,000$ & $\$2,000$ \\
    \hline
  \end{tabular}
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{G: Other Direct Costs}
%\noindent
\paragraph{\bf Materials and Supplies:} The requested materials and
supplies of \$1000 in year 1 is to partially fund a laptop or desktop computer for co-PI Moore. The computer will be used for developing the proposed algorithms and
presenting the results at conferences.
\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{H: Total Direct Costs}
%\hfill \\
%\noindent
Total of Sections A--G.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$14,130.92$ & $\$14,374.31$ & $\$14,668.63$ & $\$43,173.86
$ \\
    \hline
  \end{tabular}
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{I: Indirect Costs}
%\hfill \\
%\noindent
The US Naval Academy's federally negotiated indirect cost rate is
10\% for research on modified total direct costs (MTDC).
The base for overhead is $\$14,130.92$ in year 1, $\$14,374.31$ in
year 2, and $\$14,668.63$ in year 3.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$1,413.09$ & $\$1,437.43$ & $\$1,466.86$ & $\$4,317.38$ \\
    \hline
  \end{tabular}
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{J: Total Direct and Indirect Costs}
%\hfill \\
%\noindent
Total of Sections H and I.
%\hfill \\
\begin{center}
  \begin{tabular}{|c|c|c|c|}
    \hline
    Year 1 & Year 2 & Year 3 & Total \\
    \hline
    $\$15,544.01$ & $\$15,811.74$ & $\$16,135.49$ & $\$47,491.24$ \\
    \hline
  \end{tabular}
\end{center}



\end{document}
