\documentclass[11pt]{article}

\usepackage{color}
\usepackage{fancyhdr}
\usepackage{lastpage}
%\usepackage{amsmath,amsfonts,amssymb}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{mathpazo}

\renewcommand\thesubsection{(\alph{subsection})}
\renewcommand\thesubsubsection{(\roman{subsubsection})}

\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}
% For 11pt size

\pagestyle{fancy}
\lhead{\footnotesize Bryan Quaife}
\chead{\footnotesize Biographical Sketch}
\rhead{\footnotesize \thepage{ of }\pageref{LastPage}}
\cfoot{}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Professional Preparation}
\begin{tabular}{m{0.25\textwidth} m{0.42\textwidth} m{0.33\textwidth}}
University of Calgary & Pure and Applied Mathematics & B.Sc.~2004 \\
University of Calgary & Applied Mathematics & M.Sc.~2006 \\
Simon Fraser University & Applied and Computational Mathematics &
Ph.D.~2011 \\
University of Texas & Computational Science and Engineering & August 2011--July 2015
\end{tabular}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Appointments}
Associate \\
Geophysical Fluid Dynamics Institute \\
Florida State University \\
November 2015--\\

\noindent
Assistant Professor \\
Department of Scientific Computing \\
Florida State University \\
August 2015--\\ 

\noindent
Research Associate \\
Institute for Computational Engineering and Sciences \\
University of Texas \\
September 2014--July 2015 \\

\noindent
Postdoctoral Fellow \\
Institute for Computational Engineering and Sciences \\
University of Texas \\
September 2011--August 2014


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Publications}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Publications Most Closely Related to the Proposed
Project}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt] 
  \item Lukas Bystricy, Sachin Shanbhag, and {\bf Bryan D.~Quaife}.
    Stable and contact-free time stepping for dense rigid particle
    suspensions.  International Journal for Numerical Methods in Fluids,
    arxiv.org/abs/1804.11012, 2018.  In press

\item {\bf Bryan D.~Quaife} and M.~Nicholas J.~Moore.  A
  boundary-integral framework to simulate viscous erosion of a porous
  medium.  Journal of Computational Physics, 375:1--12, 2018.

\item Pietro de Anna, {\bf Bryan Quaife}, George Biros, and Ruben
  Juanes.  Prediction of velocity distribution from pore structure in
  simple porous media. Physical Review of Fluids, 2 (12) 124103, 2017.

\item Gokberk Kabacao\u{g}lu, {\bf Bryan Quaife}, and George Biros.
  Quantification of mixing in vesicle suspensions using numerical
  simulations in two dimensions.  Physics of Fluids, 29(2):021901, 2017.

\item MCA Kropinski and {\bf BD Quaife}. Fast integral equation methods
  for the modified Helmholtz equation. Journal of Computational Physics,
    230(2):425--434, 2011.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Other Significant Publications}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt] 

\item Gokberk Kabacao\u{g}lu, {\bf Bryan Quaife}, Bryan Quaife, and
  George Biros.  Low-resolution simulations of vesicle suspensions in
  2D. Journal of Computational Physics, 357:43--77, 2018.

\item {\bf Bryan Quaife}, Pieter Coulier, and Eric Darve. An efficient
  preconditioner for the fast simulation of a 2D Stokes flow in porous
  media. International Journal for Numerical Methods in Engineering,
  113(4):561--580, 2017. 

\item {\bf Bryan Quaife} and George Biros. Adaptive time stepping for
  vesicle simulations. Journal of Computational Physics, 306:478--499,
  2016.

\item {\bf Bryan Quaife} and George Biros. High-order adaptive time
  stepping for vesicle suspensions with viscosity contrast. Procedia
  IUTAM, 16:89–98, 2015. 

\item {\bf Bryan Quaife} and George Biros.  High-volume simulations of
  two-dimensional vesicle suspensions.  Journal of Computational
  Physics, 274:245--267, 2014.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Synergistic Activities}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt] 
  \item Organized a 2017 5-day workshop at the Banff International
    Research Station (BIRS) on complex creeping flows.

  \item Supervised two high school students for six weeks in the summer
    of 2016 through the Young Scholars Program.  They studied the effect
    that regularized kernels have on particle dynamics. 
  
  \item Supervising undergraduate projects on simulating the dynamics of
    particles on closed surfaces, simulating wildfires with cellular
    automata, and using Bayesian analysis to study ocean circulation.

  \item Organizer and co-organizer of multiple minisymposiums at SIAM
    meetings and one SIAM regional meeting.

  \item Developed the courses {\em ISC5238: Integral Equation Methods}
    and {\em ISC5935: Iterative and Direct Methods for Linear Systems}. 

\end{itemize}

\end{document}

